{\fontfamily{ptm}\selectfont Relaxed Weak Accelerated Proximal Gradient method: a unified framework for Nesterov's acceleration }

### 2025-02-27 Notebook LaTEX/Proposal/presentation.tex
>w<, changes

\documentclass[11pt]{beamer}
% PACKAGES =====================================================================
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{tcolorbox}

% THEMES AND BEAMER SETTINGS ===================================================
% \usetheme{Madrid}
\graphicspath{{.}}
\input{presets/wang/custom_commands.tex} % IMPORT WANG'S LATEX CUSTOM COMMANDS. 
\setbeamertemplate{theorems}[numbered] % ADD NUMBERING TO ALL AMS THEOREMS. 
\setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
\setbeamertemplate{blocks}[rounded][shadow=true]
% \setbeamercolor{block title}{bg=cyan,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER. 
% \setbeamercolor{block body}{bg=lime,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER.

% BIB STYLES SETTINGS ----------------------------------------------------------
\setbeamerfont{bibliography item}{size=\footnotesize}
\setbeamerfont{bibliography entry author}{size=\footnotesize}
\setbeamerfont{bibliography entry title}{size=\footnotesize}
\setbeamerfont{bibliography entry location}{size=\footnotesize}
\setbeamerfont{bibliography entry note}{size=\footnotesize}
% \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
\setbeamertemplate{navigation symbols}{}

@@

% SLIDES ELEMENTS CUSTOMIZATIONS ===============================================
\theoremstyle{definition}
\newtheorem{remark}{Remark}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}[section]
\bibliographystyle{siam}

% DOCUMENTS STARTS =============================================================
\begin{document}
\begin{frame}
    \titlepage
\end{frame}
\begin{frame}{Overview}
    This talk will be based on the content of our draft paper and selected content of the Catalyst Meta Acceleration Framework. 
    Our preprint: 
    \begin{enumerate}
        \item X. Wang and H. Li, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
    \end{enumerate}
    Catalyst Meta Acceleration:  
    \begin{enumerate}
        \item H. Lin, J. Mairal and Z. Harchaoui, \textit{A universal catalyst for first-order optimization}, in NISP, vol. 28, (2015). 
        \item \underline{\hspace{4em}}, \textit{Catalyst acceleration for first-order convex optimization: from theory to practice}, JMLR, 18 (2018), pp. 1–54.
    \end{enumerate}
\end{frame}

@@

                \item Describe for momentum sequences that doesn't follow Nesterov's rules.

@@

@@

    \subsection{Unified Convergence claim with relaxed Nesterov's sequence}
        \begin{frame}{Summary of our results}
            With the equivalent representations and the convergence claim for relaxed sequence $(\alpha_k)_{k \ge 0}$ of the R-WAPG, we are able to unify the convergence rate of: 
            \begin{enumerate}
                \item Three Euclidean variants of the FISTA algorithm. 
                \item Constant momentum APG for strongly convex objective.  
            \end{enumerate}
            The table below summarizes our major results. \begin{table}[H]
            {\tiny
            \begin{tabular}{|l|l|l|l|}
            \hline
                Algorithm & $\mu$ & $\alpha_k, \rho_k$ & $F(x_k) - F^* \le \mathcal O(\cdot)$ 
            \\ \hline
                Definition \ref{def:wapg} & 
                $\mu \ge 0$ &
                $\alpha_k \in(\mu/L, 1)$, $\rho_k > 0$ & 
                \begin{tabular}{l}
                    $\prod_{i = 0}^{k-1} \max(1, \rho_i)(1 - \alpha_{i + 1})$
                    \\
                    (Proposition \ref{prop:wagp-convergence})
                \end{tabular}
            \\ \hline
                FISTA \cite{chambolle_convergence_2015} &  
                $\mu = 0$  &
                $ 0< \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$, $\rho_k \ge 1$ &
                \begin{tabular}{l}
                    $\alpha_k^{2}$ 
                    % \\ 
                    % (Theorem \ref{thm:r-wapg-on-cham-doss})    
                \end{tabular}
            \\ \hline
                \hspace{-1em}\begin{tabular}{l}
                    V-FISTA \\ (10.7.7) \cite{beck_first-order_2017} 
                \end{tabular} &
                $\mu > 0$ &
                $\alpha_k = \sqrt{\mu/L}$, $\rho_k = 1$ & 
                \begin{tabular}{l}
                    $(1 - \sqrt{\mu/L})^k$, 
                    % \\
                    % (Theorem \ref{thm:fixed-momentum-fista}, remark)
                \end{tabular}
            \\ \hline
                Definition \ref{def:wapg} &  
                $\mu > 0$ &
                $\alpha_k = \alpha \in (\mu/L, 1)$, $\rho_k = \rho > 0$ &  
                \begin{tabular}{l}
                    $\max(1 - \alpha, 1 - \mu/(\alpha L))^{k}$
                    % \\
                    % (Theorem \ref{thm:fixed-momentum-fista})
                \end{tabular}
            \\ \hline
            \end{tabular}
            }
            \end{table}
            These results are consistent of literatures. 
            To the best of our knowledge, the last variant is, and we have the convergence claim for it using R-WAPG. 
        \end{frame}
    \subsection{A parameter free formulation of R-WAPG}
        \begin{frame}{Free R-WAPG}
            We proposed the following implementation of R-WAPG which doesn't require parameters $\mu, L$ in advance.

            \begin{algorithm}[H]
            {\scriptsize
                \begin{algorithmic}
                \STATE{\textbf{Input: } $f, g, x_0, L > \mu \ge 0, \in \RR^n, N \in \N$}
                \STATE{\textbf{Initialize: }$y_0 := x_0;L := 1; \mu := 1/2; \alpha_0 = 1;$}
                \STATE{\textbf{Compute: } $f(y_k)$; }
                \FOR{$k = 0, 1, 2, \cdots, N$}
                    \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$;}
                    \WHILE{$L/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
                        \STATE{$L:= 2L$;}
                        \STATE{$x^+ = [I + L^{-1}\partial g](y_k - L^{-1}\nabla f(y_k))$; }
                    \ENDWHILE
                    \STATE{$x_{k + 1} := x^+$;}
                    \STATE{$\alpha_{k + 1} := (1/2)\left(\mu/L - \alpha_{k}^2 + \sqrt{(\mu/L - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
                    \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
                    \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
                    \STATE{\textbf{Compute: } $f(y_{k + 1})$}
                    \STATE{$\mu := (1/2)(2D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2) + (1/2)\mu$;}
                \ENDFOR
                \end{algorithmic}
                \caption{Free R-WAPG}
                \label{alg:free-rwapg}
            }
            \end{algorithm}
        \end{frame}

@@

                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}

@@

            This is our first numerical experiment is: 
                F(x) = (1/2)\langle x, A x\rangle. 

@@

                    \caption{$N = 256$, simple convex quadratic.}

@@

                    \caption{$N = 1024$, simple convex quadratic. }

@@

            FR-WAPG estimates the following for $\mu$ during its execution: 

>>>>

\documentclass[11pt]{beamer}
% PACKAGES =====================================================================
\usepackage[utf8]{inputenc}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{subcaption}
\usepackage{tcolorbox}
\usepackage{wrapfig}

% THEMES AND BEAMER SETTINGS ===================================================
% \usetheme{Madrid}
\graphicspath{{.}}
\input{presets/wang/custom_commands.tex} % IMPORT WANG'S LATEX CUSTOM COMMANDS. 
\setbeamertemplate{theorems}[numbered] % ADD NUMBERING TO ALL AMS THEOREMS. 
\setbeamertemplate{footline}[frame number] % ADD PAGE NUMBERS ON BOTTOM. 
\setbeamertemplate{blocks}[rounded][shadow=true]
\setbeamertemplate{navigation symbols}{} 
% \setbeamercolor{block title}{bg=cyan,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER. 
% \setbeamercolor{block body}{bg=lime,fg=black} % CHANGE THE BLOCK STYLE IN BEAMER.

% BIB STYLES SETTINGS ----------------------------------------------------------
\setbeamertemplate{bibliography item}{\insertbiblabel}
\setbeamerfont{bibliography item}{size=\footnotesize}
\setbeamerfont{bibliography entry author}{size=\footnotesize}
\setbeamerfont{bibliography entry title}{size=\footnotesize}
\setbeamerfont{bibliography entry location}{size=\footnotesize}
\setbeamerfont{bibliography entry note}{size=\footnotesize}
% \setbeamercovered{transparent}  % GREY OUT PAUSED FUTURE ITEMS IN SLID. 
\bibliographystyle{siam}

@@

% SLIDES ELEMENTS CUSTOMIZATIONS ===============================================
\theoremstyle{definition}
\newtheorem{remark}{Remark}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{proposition}{Proposition}[section]

% DOCUMENTS STARTS =============================================================
\begin{document}
\begin{frame}
    \titlepage
\end{frame}
\begin{frame}{Overview}
    This talk will be based on the content of our draft paper and selected content of the Catalyst Meta Acceleration Framework. 
    Our preprint: 
    \begin{enumerate}
        \item H. Li and X. Wang, \textit{A Parameter Free Accelerated Proximal Gradient Method Without Restarting}, preprint, (2025).
    \end{enumerate}
    Catalyst Meta Acceleration:  
    \begin{enumerate}
        \item H. Lin, J. Mairal and Z. Harchaoui, \textit{A universal catalyst for first-order optimization}, in NISP, vol. 28, (2015). 
        \item \underline{\hspace{4em}}, \textit{Catalyst acceleration for first-order convex optimization: from theory to practice}, JMLR, 18 (2018), pp. 1–54.
    \end{enumerate}
\end{frame}

@@

                \item Gives upper bound for $F(x_k) - \inf_{x \in \RR^n} F(x)$ for momentum sequences that doesn't follow Nesterov's rules.

@@

        \begin{frame}{R-WAPG Assumptions and Notations}
            \begin{assumption}\label{ass:regret-gap}
                Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
                \begin{align}
                    g_k &\defeq L(y_k - T_L(y_k)), 
                    \label{eqn:grad-map}
                    l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
                    \label{eqn:lower-linearization}
                    \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k). 
                    \label{eqn:regret}

@@

    \subsection{Unified Convergence claim with relaxed Nesterov's sequence}
        \begin{frame}{Summary of our results}
            With the equivalent representations and the convergence claim for relaxed sequence $(\alpha_k)_{k \ge 0}$ of the R-WAPG, we are able to unify the convergence rate of: 
                \item Three Euclidean variants of the FISTA algorithm. 
                \item Constant momentum APG for strongly convex objective.  
            The table below summarizes our major results. \begin{table}[H]
            {\tiny
            \begin{tabular}{|l|l|l|l|}
            \hline
                Algorithm & $\mu$ & $\alpha_k, \rho_k$ & $F(x_k) - F^* \le \mathcal O(\cdot)$ 
            \\ \hline
                Definition \ref{def:wapg} & 
                $\mu \ge 0$ &
                $\alpha_k \in(\mu/L, 1)$, $\rho_k > 0$ & 
                \begin{tabular}{l}
                    $\prod_{i = 0}^{k-1} \max(1, \rho_i)(1 - \alpha_{i + 1})$
                    (Proposition \ref{prop:wagp-convergence})
                \end{tabular}
            \\ \hline
                FISTA \cite{chambolle_convergence_2015} &  
                $\mu = 0$  &
                $ 0< \alpha_k^{-2} \le \alpha_{k + 1}^{-1} - \alpha_{k + 1}^{-2}$, $\rho_k \ge 1$ &
                \begin{tabular}{l}
                    $\alpha_k^{2}$ 
                    % \\ 
                    % (Theorem \ref{thm:r-wapg-on-cham-doss})    
                \end{tabular}
            \\ \hline
                \hspace{-1em}\begin{tabular}{l}
                    V-FISTA \\ (10.7.7) \cite{beck_first-order_2017} 
                \end{tabular} &
                $\mu > 0$ &
                $\alpha_k = \sqrt{\mu/L}$, $\rho_k = 1$ & 
                \begin{tabular}{l}
                    $(1 - \sqrt{\mu/L})^k$, 
                    % \\
                    % (Theorem \ref{thm:fixed-momentum-fista}, remark)
                \end{tabular}
            \\ \hline
                Definition \ref{def:wapg} &  
                $\mu > 0$ &
                $\alpha_k = \alpha \in (\mu/L, 1)$, $\rho_k = \rho > 0$ &  
                \begin{tabular}{l}
                    $\max(1 - \alpha, 1 - \mu/(\alpha L))^{k}$
                    % \\
                    % (Theorem \ref{thm:fixed-momentum-fista})
                \end{tabular}
            \\ \hline
            \end{tabular}
            \end{table}
            These results are consistent of literatures. 
            To the best of our knowledge, the last variant is, and we have the convergence claim for it using R-WAPG. 
    \subsection{A parameter free formulation of R-WAPG}
        \begin{frame}{Free R-WAPG}
            We proposed the following implementation of R-WAPG which doesn't require parameters $\mu, L$ in advance. 
            \begin{algorithm}[H]
                \begin{algorithmic}[1]
                \STATE{\textbf{Input: } $f, g, L > \mu \ge 0, x_0 \in \RR^n, N \in \N$}
                \STATE{\textbf{Initialize: }$y_0 := x_0;L_0 := 1; \mu_0 := 1/2; \alpha_0 = 1$;}
                \STATE{\textbf{Compute: } $f(y_k)$; }
                \FOR{$k = 0, 1, 2, \cdots, N$}
                    \STATE{\textbf{Compute: }$\nabla f(y_k); x^+:= [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$;}
                    \WHILE{$L_k/2\Vert x^+ - y_k\Vert^2 < D_f(x^+, y_k)$}
                        \STATE{$L_k:= 2L_k$;}
                        \STATE{$x^+ = [I + L_k^{-1}\partial g]^{-1}(y_k - L_k^{-1}\nabla f(y_k))$; }
                    \ENDWHILE
                    \STATE{$x_{k + 1} := x^+$;}
                    \STATE{$\alpha_{k + 1} := (1/2)\left(\mu_k/L_k - \alpha_{k}^2 + \sqrt{(\mu_k/L_k - \alpha_{k}^2)^2 + 4\alpha_{k}^2}\right)$;}
                    \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}
                    \STATE{$y_{k + 1}:= x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$; }
                    \STATE{\textbf{Compute: } $f(y_{k + 1})$}
                    \STATE{$\mu_k := D_f(y_{k + 1}, y_{k})/\Vert y_{k + 1} - y_k\Vert^2 + (1/2)\mu_k$;}
                \ENDFOR
                \end{algorithmic}
                \caption{Free R-WAPG}
                \label{alg:free-rwapg}
            \end{algorithm}

@@

                \NOG_k := \frac{F(x_k) - F^*}{F(x_0) - F^*}.

@@

            Consider objective function: $F(x) = (1/2)\langle x, A x\rangle$. 

@@

                    \caption{$N = 256$.}

@@

                    \caption{$N = 1024$.}

@@

            FR-WAPG estimates the following for $\mu_k$: 

### 2025-02-27 Notebook LaTEX/R-WAPG/paper3.tex
>w<, changes

\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{true}
\input{presets/wang/input.tex}
\input{presets/misc.tex}
\input{presets/julia_lstlisting.tex}

@@

\title{{\fontfamily{ptm}\selectfont 
        A Parameter Free Accelerated Proximal Gradient Method Without Restarting
    }}

@@

    \begin{lemma}[Proximal gradient envelope]\label{lemma:pg-envelope}

@@

            \mathcal M^{L^{-1}}(x; y)- D_f(x, y) \le \mathcal M^{L^{-1}}(x; y). 

@@

\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
    \par 
    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm. 
    It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
    \par
    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
    \begin{assumption}\label{ass:regret-gap}
        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L(y_k)), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k), 
            \label{eqn:regret}
        \end{align}
        % To see $\epsilon_k \ge 0$, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$, by the definition $g_k = L(y_k - T_L(y_k))$ it has: 
        % \begin{align*}
        %     F(x_k) - F(T_L(y_k))
        %     - \langle L(y_k - T_L(y_k)),x_k - y_k \rangle
        %     - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
        %     - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     F(x_k) - F(T_L(y_k))
        %     - \langle g_k,x_k - y_k \rangle
        %     - \frac{1}{2L}\Vert g_k\Vert^2
        %     &\ge 0. 
        % \end{align*}
    \end{assumption}

@@

    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
        Consider the algorithm with a constant momentum specified by the following: 
        \begin{tcolorbox}
            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
            \\
            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
            \begin{align*}
                &x_{k + 1} = y_k + L^{-1}\mathcal G_L (y_k)
                , 
                \\
                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
            \end{align*}
        \end{tcolorbox}
        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$. 
    \end{theorem}
    \begin{proof}
        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
        The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}. 
        Then, Proposition \ref{prop:wapg-convergence} applies,and it follows that: 
        \begin{align*}
            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(
                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right)\right)^k
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
            \right). 
            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
        \end{align*}
        Going from the second last to the last equality, we used the initialization condition $y_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, therefore it has $v_1 = x_1$. 
    \end{proof}
    \begin{remark}
        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex stronlgy convex function and all possible $\alpha_k \in (\mu/L, 1)$. 
        In addition, the convergence claim of R-WAPG holds for any $\mu$ smaller than the strong convexity modulus of $f$ that is not zero making the bounds $r \in (\sqrt{q}, \sqrt{q^{-1}})$ looser. 
    \end{remark}

@@

    To prvent the case $\alpha_k = 1$, we may always force the esimate $\mu = L/2$ whenever $\mu > L/2$. 

@@

            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specifice initial condition. 

@@

            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gaph $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}. 

@@

                \caption{A single LASSO experiment results, with $M = 64, N=256$. }

>>>>

\usepackage{ifthen}\newboolean{draftmode}\setboolean{draftmode}{false}
\input{presets/wang/input.tex}
% \input{presets/misc.tex}
% \input{presets/julia_lstlisting.tex}

@@

\title{{\fontfamily{ptm}\selectfont 
        % A Parameter Free Accelerated Proximal Gradient Method Without Restarting
        Relaxed Weak Accelerated Proximal Gradient method: a unified framework for Nesterov's acceleration
    }}

@@

    \begin{lemma}\label{lemma:pg-envelope}

@@

            \mathcal M^{L^{-1}}(x; y)- D_f(x, y). 

@@

\section{Stepwise formulation of weak accelerated proximal gradient}\label{sec:stepwise-stuff}
    The goal of this section is to build the R-WAPG algorithm which is described in the Definition \ref{def:wapg} of the next section. 
    \par 
    Definition \ref{def:stepwise-wapg} describes one iteration of the R-WAPG algorithm. 
    It defines the procedure of generating $x_{k + 1}, v_{k + 1}$ given any $x_k, v_k$. 
    Proposition \ref{prop:stepwise-lyapunov} states the inequality \eqref{ineq:stepwise-lya-2}  of a decreasing quantity involving $F(x_k), F(x_{k + 1})$ at each iteration.
    \par
    The assumption below is crucial to describing the convergence rate of the R-WAPG and it requires the convexity assumption on $F$. 
    \begin{assumption}\label{ass:regret-gap}
        Given $x_k, y_k, v_k$ where $k \in \mathbb Z_+$, we define the following quantities
        \begin{align}
            g_k &\defeq L(y_k - T_L(y_k)), 
            \label{eqn:grad-map}
            \\
            l_F(x; y_k) &\defeq F(T_L(y_k)) + \langle g_k, x - y_k\rangle + \frac{1}{2L}\Vert g_k\Vert^2, 
            \label{eqn:lower-linearization}
            \\
            \epsilon_{k} &\defeq F(x_k) - l_F(x_k; y_k). 
            \label{eqn:regret}
        \end{align}
        % To see $\epsilon_k \ge 0$, use Theorem \ref{thm:prox-grad-ineq} and let $y = y_k, x = x_k$, by the definition $g_k = L(y_k - T_L(y_k))$ it has: 
        % \begin{align*}
        %     F(x_k) - F(T_L(y_k))
        %     - \langle L(y_k - T_L(y_k)),x_k - y_k \rangle
        %     - \frac{L}{2}\Vert y_k - T_Ly_k\Vert^2
        %     - \frac{\mu}{2}\Vert x_k - y_k\Vert^2
        %     &\ge 0
        %     \\
        %     \iff 
        %     F(x_k) - F(T_L(y_k))
        %     - \langle g_k,x_k - y_k \rangle
        %     - \frac{1}{2L}\Vert g_k\Vert^2
        %     &\ge 0. 
        % \end{align*}
    \end{assumption}

@@

    \begin{theorem}[Fixed momentum APG]\label{thm:fixed-momentum-fista}
        Assume $L > \mu > 0$, let a pair of constant R-WAPG sequence: $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be given by Lemma \ref{lemma:constant-rwapg-seq}.
        Define $q := \mu/L$ and for any fixed $r \in \left(\sqrt{q}, \sqrt{q^{-1}}\right)$, let $\alpha_k := \alpha = r \sqrt{q}$ be the constant R-WAPG sequence. 
        Consider the algorithm with a constant momentum specified by the following: 
        \begin{tcolorbox}
            Define $\theta = \left(1 - r^{-1}\sqrt{q}\right)(1 - r\sqrt{q})(1 - q)^{-1}$. 
            \\
            Initialize $y_1 = x_1$; for $k = 1, 2, \ldots, N$, update: 
            \begin{align*}
                &x_{k + 1} = y_k + L^{-1}\mathcal G_L (y_k)
                , 
                \\
                & y_{k + 1} = x_{k + 1} + \theta(x_{k + 1} - x_k). 
            \end{align*}
        \end{tcolorbox}
        Then the algorithm generates $(x_k)_{k \ge 1}$ such that $F(x) - F(x^*)$ convergences at a rate of $\mathcal O\left(\left(1 - \min\left(\mu/(\alpha L), \alpha\right)\right)^k\right)$. 
    \end{theorem}
    \begin{proof}
        The constant sequence $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ is a valid R-WAPG sequence by Lemma \ref{lemma:constant-rwapg-seq}. 
        The algorithm presented here is the same as the R-WAPG momentum form as given by Definition \ref{def:r-wapg-momentum-form} because the term $\theta$ from Lemma \ref{lemma:constant-rwapg-seq} matches up with Definition \ref{def:r-wapg-momentum-form} by (ii) in Lemma \ref{lemma:constant-rwapg-seq}. 
        Then, Proposition \ref{prop:wapg-convergence} applies, and it follows that: 
        \begin{align*}
            & F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert v_{k + 1} - x^*\Vert^2
            \\
            &= 
            F(x_{k + 1}) - F^* + \frac{L\alpha_k^2}{2}\Vert x_{k + 1}  - x^* + (\alpha^{-1} - 1)(x_{k + 1} - x_k)\Vert^2
            \\
            &\le 
            \left(
                \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
            \right)
            \left(
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(
                \prod_{i = 1}^{k - 1} \max(1, \rho)(1 - \alpha)
            \right)
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2
            \right)
            \\
            &= \left(1 - \min\left(\frac{\mu}{\alpha L}, \alpha\right)\right)^k
            \left(
                F(x_1) - F(x^*) + \frac{L\alpha_0^2}{2}\Vert x_1 - x^*\Vert^2
            \right). 
            & \text{Lemma \ref{lemma:constant-rwapg-seq} (v)}
        \end{align*}
        Going from the second last to the last equality, we used the initialization condition $y_1 = x_1$ specified in Proposition \ref{prop:r-wapg-momentum-repr}, therefore it has $v_1 = x_1$. 
    \end{proof}
    \begin{remark}
        When $r = 1$, the algorithm described above is exactly the same as the V-FISTA algorithm specified in (10.7.7) of Beck's book \cite{beck_first-order_2017}. 
        The above theorem gives convergence rate for a much relax choice of momentum parameter $\theta$ generalizing the convergence of constant step size FISTA to all convex and strongly convex function and all possible $\alpha_k \in (\mu/L, 1)$. 
        In addition, the convergence claim of R-WAPG holds for any $\mu$ smaller than the strong convexity modulus of $f$ that is not zero making the bounds $r \in (\sqrt{q}, \sqrt{q^{-1}})$ looser. 
    \end{remark}

@@

    To prevent the case $\alpha_k = 1$, we may always force the estimate $\mu = L/2$ whenever $\mu > L/2$. 

@@

            Figure \ref{fig:simple-quadratic-r-wapg-mu-estimates} shows the estimated $\mu_k$ of FR-WAPG on the left and the convergence rate of the test algorithms on the right for one specific initial condition. 

@@

            In addition, an experiment were conducted to show the estimate $\mu_k$ and optimality gap $F(x_k) - F^*$ in Figure \ref{fig:single-lass-mu-estimates}. 

@@

                \caption{A single LASSO experiment results, with $M = 64, N=256$. f}
